A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-11 application_to_path_tracing.tex
Petite correction de reference

The skeleton of the void is computed with our algorithm \ref{sec::skeletonization} and is converted to a graph (the nodes are 3D positions and the edges represents the topology of the scene), given as an input of our path tracing. We then compute a set of points called \myem{importance points}. These points will be used to sample $\Omega_x$ in the path tracing algorithm. For each node of the skeleton $n$, one importance point $imp_n$ is computed.

>>>>

The skeleton of the void is computed with our algorithm (section \ref{sec::skeletonization}) and is converted to a graph (the nodes are 3D positions and the edges represents the topology of the scene), given as an input of our path tracing. We then compute a set of points called \myem{importance points}. These points will be used to sample $\Omega_x$ in the path tracing algorithm. For each node of the skeleton $n$, one importance point $imp_n$ is computed.
